Learning and calibrating per-location classifiers for visual place recognition\thanks{

### 2015-12-03 manuscript.tex
minor eidts

      As a query set with known ground truth GPS positions, we use 8999 panoramas from the Google Street View research dataset~\cite{GoogleResearch}, which cover approximately the same area, but were captured at a different time, and typically depict the same places from different viewpoints and under different illumination conditions.          
      We generate a test query set such that we first select a panorama at random, and second, we generate a perspective image with a random orientation and random elevation pitch. This way we synthesize 4,000 query test images. Both the query and database images are available upon request at~\cite{GronatProjectPage}.

>>>>

      As a query set with known ground truth GPS positions, we use 8999 panoramas from the Google Street View research dataset~\cite{GoogleResearch}, which cover approximately the same area, but were captured at a different time. The query images typically depict the same places from different viewpoints and under different illumination conditions.          
      We generate a test query set such that we first select a panorama at random, and second, we generate a perspective image with a random orientation and random elevation pitch. This way we synthesize 4,000 query test images. Both the query and database images are available upon request at~\cite{GronatProjectPage}.
